Title

### 2023-10-17 main.tex
increased loading time by a bit

% Use "Eq" instead of "Equation" for equation citations.
% }}}

@@

{\color{green}
Pauli channels are fundamental in the context of quantum computing as they
model the simplest kind of noise in quantum devices, and
Pauli dynamical maps are parametrized Pauli channels,
which can model a continuous transformation of a quantum device.
In this article, we propose a quantum
algorithm for simulating
Pauli dynamical maps
by using a parametrized quantum circuit.
We also establish the mathematical conditions for an
$N$-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is reported. 
}
\section{Introduction} % {{{

@@

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts towards the
simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.

@@

\revnote{I fail to see the point here - the logic of the paper is: 
1."open quantum systems can be modeled through a class of channels representing he various types of decoherence. 2. Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.
3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them. \\
What I am missing is what do we learn by doing it which can't be learned by actually performing the Pauli channel onto a quantum system? For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial. Why would I need to decompose (not even effectively for any channel) the Pauli channels to match a gate based description? Which class of problems can we simulate that cannot be simulated otherwise? Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)\\
Intuitively, it seems incredibly harder resource wise to create the sum $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}

\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma
similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
La verdad no sé bien cómo contestar a este comentario. \\
Una forma podria ser cambiar un poco el enfoque. 
Hacer que el objetivo principal sea
simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y estudiar como entra el parámetro en juego. 
Luego, decir que para simular mapas parametrizados de Pauli,
necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
pero lo bueno es que es un mismo algorigmo para todos, lo que 
nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
poder reducir el número de parámetros, con lo que
llegamos al teorema de los circuitos 1PR y etc.
También corremos el circuito en computadoras cuánticas,
lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
haber usado compus cuanticas. \\
Al final, también recalcar que el resutlado sobre 1PR es más
general que solo canales de Pauli y puede ser útil
para cualquier curcuito parametrizado.} \\
$\;$ \\
Ahora sí la nueva propuesta de la intro (los primeros dos párrafos son iguales): \\
$\;$ \\
{\color{green}

>>>>

% Use "Eq" instead of "Equation" for equation citations.

@@

{\color{green}
Pauli channels are fundamental in the context of quantum computing as they
model the simplest kind of noise in quantum devices, and
Pauli dynamical maps are parametrized Pauli channels,
which can model a continuous transformation of a quantum device.
In this article, we propose a quantum
algorithm for simulating
Pauli dynamical maps
by using a parametrized quantum circuit.
We also establish the mathematical conditions for an
$N$-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is reported. 
}
% }}}
\section{Introduction} % {{{

@@

@@

\revnote{I fail to see the point here - the logic of the paper is: % {{{
1."open quantum systems can be modeled through a class of channels representing
he various types of decoherence. 2. Quantum circuits are a convenient
gate-based formalism that is well understood and has an extensive body of work,
and experimentally accessible.  3. We map (generalised) Pauli channels onto
quantum circuits, as a way to simulate them. \\
What I am missing is what do we learn by doing it which can't be learned by
actually performing the Pauli channel onto a quantum system? For example,
applying well controlled sx, sy, sz operations and their coherent parametric
combination using a photonic polarisation or path encoding is experimentally
trivial. Why would I need to decompose (not even effectively for any channel)
the Pauli channels to match a gate based description? Which class of problems
can we simulate that cannot be simulated otherwise? Is there any advantage (for
example in speed up, resources like ancillas required, resistance to unwanted
noise etc..?)\\
Intuitively, it seems incredibly harder resource wise to create the sum
$b|gamma\rangle$ superposition state needed for the ancilla, just for the sake
of having it into a "quantum circuit" perspective.} % }}}
\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma % {{{
similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
La verdad no sé bien cómo contestar a este comentario. \\
Una forma podria ser cambiar un poco el enfoque. 
Hacer que el objetivo principal sea
simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y
estudiar como entra el parámetro en juego. 
Luego, decir que para simular mapas parametrizados de Pauli,
necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
pero lo bueno es que es un mismo algorigmo para todos, lo que 
nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
poder reducir el número de parámetros, con lo que
llegamos al teorema de los circuitos 1PR y etc.
También corremos el circuito en computadoras cuánticas,
lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
haber usado compus cuanticas. \\
Al final, también recalcar que el resutlado sobre 1PR es más
general que solo canales de Pauli y puede ser útil
para cualquier curcuito parametrizado.} % }}}

Ahora sí la nueva propuesta de la intro (los primeros dos párrafos son iguales): \\
$\;$ \\
{\color{green}
